\LARGE \bf Steering a Swarm Using Global Inputs And Swarm Statistics

### 2016-08-06 journalSwarmControl/realExperiment.tex
Added Policy Iteration Algorithm
Added the mean image

The objects were 3D printed from ABS plastic. Laser-cut patterns for the neon green fiducial markers on the robots and {\sc Matlab} tracking code are available at our github repository~\cite{Shahrokhi2015GitHubShapeControl}.
\begin{figure*}
\begin{center}
	%\includegraphics[width=0.5\columnwidth]{SetUp.pdf}
	\begin{overpic}[width=0.49\columnwidth]{SetUp.pdf}\put(1,75){a)}\end{overpic}
	\begin{overpic}[width=0.35\columnwidth]{MainExpFig.pdf}\put(5,92){b)}\end{overpic}
\end{center}

\caption{\label{fig:setup}
Hardware platform:  table with 1.5$\times$1.2 m workspace, surrounded by eight remotely triggered 30W LED floodlights, with an overhead machine vision system (Left). A swarm of robots, all controlled by a uniform force field, can be effectively controlled by a hybrid controller that knows only the first and second moments of the robot distribution.  Here is a swarm of hardware robots (kilobots) that pushes a green hexagon toward the goal (Right). See video attachment~\cite{ShivaVideo2015}
}
\end{figure*}

@@

\begin{figure*}
\begin{center}
	\begin{overpic}[width=0.6\columnwidth]{Mean_Control_experiment.eps}\end{overpic}
	\begin{overpic}[width=0.35\columnwidth]{XYMeanControl.eps}\end{overpic}
\end{center}
\caption{\label{fig:realMean}
Mean control plot with kilobots. \todo{place a red star and a red circle at two spots on graph, put two images of the swar at right with a red star and red crcle in left hand corner of these, and put a scale bar in image}
}
\end{figure*}

>>>>

The objects were 3D printed from ABS plastic. Laser-cut patterns for the neon green fiducial markers on the robots and {\sc Matlab} tracking code are available at our github repository~\cite{Shahrokhi2015GitHubShapeControl}.
\begin{figure*}
\begin{center}
	%\includegraphics[width=0.5\columnwidth]{SetUp.pdf}
	\begin{overpic}[width=0.49\columnwidth]{SetUp.pdf}\put(1,75){a)}\end{overpic}
	\begin{overpic}[width=0.3\columnwidth]{TestedShapesR.pdf}\put(5,85){b)}\end{overpic}
\end{center}

\caption{\label{fig:setup}
Hardware platform:  table with 1.5$\times$1.2 m workspace, surrounded by eight remotely triggered 30W LED floodlights, with an overhead machine vision system (Left). A swarm of robots, all controlled by a uniform force field, can be effectively controlled by a hybrid controller that knows only the first and second moments of the robot distribution.  Here is a swarm of hardware robots (kilobots) that pushes a green hexagon or a green circle toward the goal (Right). See video attachment~\cite{ShivaVideo2015}
}
\end{figure*}

@@

\begin{figure*}
\begin{center}
	\begin{overpic}[width=\columnwidth]{RealMean}\end{overpic}
%	\begin{overpic}[width=0.35\columnwidth]{XYMeanControl.eps}\end{overpic}
\end{center}
\caption{\label{fig:realMean}
Mean control plot with kilobots. %\todo{place a red star and a red circle at two spots on graph, put two images of the swar at right with a red star and red crcle in left hand corner of these, and put a scale bar in image}
}
\end{figure*}
